Figure 3a

### 2017-11-21 inst/stable_line_expression/stable_line_expression.Rmd
fixing figures after last commit

vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI ==    "miR34a" ~ 1 + 0.25,
      GOI == "miR34a asRNA" ~ 1 - 0.25
    ),
    xend = case_when(
      GOI ==    "miR34a" ~ 2 + 0.25,
      GOI == "miR34a asRNA" ~ 2 - 0.25
    )
  ) %>%
  inner_join(ys) %>%
  mutate(
    max = max + c(0.25, 1.25, 0.25, 1.25, 0.25, 1.25)
  )
```

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.4, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 1.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

>>>>

vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI ==    "miR34a" ~ 1 + 0.25,
      GOI == "miR34a asRNA" ~ 1 - 0.25
    ),
    xend = case_when(
      GOI ==    "miR34a" ~ 2 + 0.25,
      GOI == "miR34a asRNA" ~ 2 - 0.25
    )
  ) %>%
  inner_join(ys) %>%
  mutate(
    max = max + c(0.55, 1.95, 0.25, 1.65, 0.25, 1.65)
  )
```

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.6, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 1.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 60,
   width = 83,
   units = "mm"
)
```
